Appendix 1: Preregistered analysis with simulated data

### 2025-04-28 preregistration.Rmd
dates

A set of blood donors will be randomly selected from all blood donors in FRCBS register who have donated at least once during the 730 preceding the day the questionnaire e-mail will be sent i.e. 5.5.2025 .

@@

The online questionnaire will be open for 2 weeks i.e. from 5.5.2025 to 18.5.2025.

>>>>

A set of blood donors will be randomly selected from all blood donors in FRCBS register who have donated at least once during the 730 preceding the day the questionnaire e-mail will be sent in May 2025 .

@@

The online questionnaire will be open for 2 weeks.
